\section{Library for data analysis}
\label{libra}
In this section, some of the classes implemented in the library are listed. Classes omitted are Scatterplot, Lineplot and Distribuzioni that allow a suitable print of data obtainable by the following classes.

\subsection{class Node}
A class that realize the concept of node.
\subsubsection{node.hpp}
\lstinputlisting[language=C++,style=customc]{codice/libreria/node.hpp}
\vspace{0.5cm}
\subsubsection{node.cpp}
\lstinputlisting[language=C++,style=customc]{codice/libreria/node.cpp}
\vspace{0.5cm}

\subsection{class Graph}
The class Graph is central for the library. It allows to obtain all main quantities about a graph, or a tree.
\subsubsection{graph.hpp}
\lstinputlisting[language=C++,style=customc]{codice/libreria/graph.hpp}
\vspace{0.5cm}
\subsubsection{graph.cpp}
\lstinputlisting[language=C++,style=customc]{codice/libreria/graph.cpp}
\vspace{0.5cm}

\subsection{class Packagegraph}
This class is a tool that allows to analyze automatically more graphs at the same time.
\subsubsection{packagegraph.hpp}
\lstinputlisting[language=C++,style=customc]{codice/libreria/packagegraph.hpp}
\vspace{0.5cm}
\subsubsection{packagegraph.cpp}
\lstinputlisting[language=C++,style=customc]{codice/libreria/packagegraph.cpp}
\vspace{0.5cm}

\subsection{class Treemaker}
This class builds trees and graphs through Sharing Tree model, Pang-Maslov model and Branching Tree model.
\subsubsection{treemaker.hpp}
\lstinputlisting[language=C++,style=customc]{codice/libreria/treemaker.hpp}
\vspace{0.5cm}
\subsubsection{treemaker.cpp}
\lstinputlisting[language=C++,style=customc]{codice/libreria/treemaker.cpp}
\vspace{0.5cm}

\comment{
\subsection{class Distribuzioni}
This class calculates distributions about all main quantities in this analysis.
\subsubsection{distribuzioni.hpp}
\lstinputlisting[language=C++,style=customc]{codice/libreria/distribuzioni.hpp}
\vspace{0.5cm}
\subsubsection{distribuzioni.cpp}
\lstinputlisting[language=C++,style=customc]{codice/libreria/distribuzioni.cpp}
\vspace{0.5cm}

\subsection{class Scatterplot}
Scatterplots have a fundamental role in this analysis. This class allows to obtain all scatterplots contained in this thesis.
\subsubsection{scatterplot.hpp}
\lstinputlisting[language=C++,style=customc]{codice/libreria/scatterplot.hpp}
\vspace{0.5cm}
\subsubsection{scatterplot.cpp}
\lstinputlisting[language=C++,style=customc]{codice/libreria/scatterplot.cpp}
\vspace{0.5cm}

\subsection{class Lineplot}
While distributions and scatterplots are done for the whole dataset, the class Lineplot allows to obtain an analysis from each graph.
\subsubsection{treemaker.hpp}
\lstinputlisting[language=C++,style=customc]{codice/libreria/lineplot.hpp}
\vspace{0.5cm}
\subsubsection{treemaker.cpp}
\lstinputlisting[language=C++,style=customc]{codice/libreria/lineplot.cpp}
\vspace{0.5cm}

\subsection{Tools}
Miscellaneous tools for the library.
\subsubsection{funzioni.hpp}
\lstinputlisting[language=C++,style=customc]{codice/libreria/funzioni.hpp}
\vspace{0.5cm}
\subsubsection{funzioni.cpp}
\lstinputlisting[language=C++,style=customc]{codice/libreria/funzioni.cpp}
\vspace{0.5cm}
\subsubsection{libreria.hpp}
\lstinputlisting[language=C++,style=customc]{codice/libreria/libreria.hpp}
\vspace{0.5cm}
\subsubsection{Uniqa}
\lstinputlisting[language=bash,style=customc]{codice/programmi/Uniqa}
\vspace{0.5cm}
\subsubsection{Sorta}
\lstinputlisting[language=bash,style=customc]{codice/programmi/Sorta}
}

\section{Programs for simulations and analysis}

\subsection{mrmodel.cpp}
This program use the library to simulate and analyze Sharing Trees.
\lstinputlisting[language=C++,style=customc]{codice/libreria/mrmodel.cpp}
\vspace{0.5cm}

\subsection{tarantola.cpp}
A program to obtain the whole data analysis through the library.
\lstinputlisting[language=C++,style=customc]{codice/libreria/tarantola.cpp}
\vspace{0.5cm}


\section{Programs for data conversion}
\label{app}
Programs in this section are written in gvpr \cite{gvpr}.
\subsection{Papera.gv}
A program to paste together the subgraphs produced by doxygen.
\lstinputlisting[language=awk,style=customc]{codice/script/Papera.gv}
\vspace{0.5cm}

\subsection{Bilimetta.gv}
A program to erase templates from graphs.
\lstinputlisting[language=awk,style=customc]{codice/script/Bilimetta.gv}
\vspace{0.5cm}

\subsection{Numerello.gv}
A program to convert .dot files in adjacency lists.
\lstinputlisting[language=awk,style=customc]{codice/script/Numerello.gv}


